\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\title{Meta Analysis}
\author{Travis Andersen }
\date{November 2020}

\begin{document}

\maketitle

\section{Frameworks}

\begin{itemize}

    \item Fixed effect: The studies are assumed to investigate the same
    population, use the same variable and outcome definitions, etc.

    \item Random effects: The studies are assumed to be heterogeneous

\end{itemize}

\section{Models}

We are considering the case where there are k independent studies done,
resulting in k 2 x 2 tables as shown below. The parameter of interest in these
cases is often the odds ratio, defined as $OR = \frac{a/b}{c/d} = \frac{ad}{bc}$.
We are comparing different methods of pooling the odds ratios.

\begin{table}[h!]
\centering
    \begin{tabular}{|c|c|}
        \hline
        a & b \\
        \hline
        c & d \\
        \hline
    \end{tabular}
\caption{2 x 2 table}
\end{table}

Following are several common models for pooling the odds ratios.

\subsection{Inverse Variance}

\begin{equation}
    \hat{OR}_{pooled} = \frac
    {\sum_{i=1}^k \text{Var}(\frac{a_i d_i}{b_i c_i})^{-1} \frac{a_i d_i}{b_i c_i}}
    {\sum_{i=1}^k \text{Var}(\frac{a_i d_i}{b_i c_i})^{-1}}
\end{equation}

\begin{itemize}
  \item Assumes fixed effect framework.
\end{itemize}

\subsection{DerSimonian-Laird}

\begin{equation}
    \hat{OR}_{pooled} =
\end{equation}

\begin{itemize}
  \item Assumes random effects framework.
  \item Adaption of inverse variance for random effects framework.
  \item Most common for medical and psychological research
  \item Prone to producing false positives, especially when the number of
  studies is small
\end{itemize}

\subsection{Mantel-Haenszel}

\begin{equation}
    \hat{OR}_{pooled} = \frac
    {\sum_{i=1}^k \frac{a_i d_i}{n_i}}
    {\sum_{i=1}^k \frac{b_i c_i}{n_i}},
    \text{where } n_i = a_i + b_i + c_i + d_i
\end{equation}

\begin{itemize}
  \item Assumes fixed effect framework
  \item Better at binary outcomes than inverse variance.
\end{itemize}

\subsection{Peto}

\begin{equation}
    \hat{OR}_{pooled} = \text{exp}
    (\frac{\sum_{i=1}^k (O_i - E_i)}{\sum_{i=1}^k V_i})
\end{equation}

O, E, and V are defined such that $O = a$, $E = \frac{(a+b)(a+c)}{n}$, and
$V = \frac{(a+b)(c+d)(a+c)(b+d)}{n^2(n-1)}$ (where $n = a+b+c+d$).

\begin{itemize}
  \item Assumes fixed effect framework
  \item Only used for odds ratios
  \item Works best when odds ratios are close to one
  \item Performs well for rare events
  \item Can cause bias when samples are very unbalanced
  \item Corrections for zero cell counts are not necessary
\end{itemize}

\end{document}
